Authors: Tat and Chrysie
Date: 30/4/2024
Purpose: crying
Version: 1
Notes: it worked when andrea pointed out the obvious

# loading the script

``` {r}
#install.packages("foreign")
library(foreign)
#OR
install.packages("haven")
library(haven)

st_data <- foreign::read.spss('../data/SchoolTransitionData.sav', to.data.frame = T)

# saving the spss dataframe as a csv because excel supremacy
output_path <- "../data/st_data.csv"  
write.csv(st_data, file = output_path, row.names = TRUE)

```

# getting our data separate

``` {r}
# loading the data into my environment
st_data <- read.csv("../data/st_data.csv")

# variable column codes
{
**X** = ppt number

**ID** = ppt ID

#### [**SDQ**]{.underline} 

-   Child Wave 1: C1_B1 to 25 - recode: 7, 11, 14, 21, 25

-   Child Wave 2: C2_B1 to 25 - recode: 7, 11, 14, 21, 25

-   Child Wave 3: C3_B1 to 25 - recode: 7, 11, 14, 21, 25
  
  # Not True = 0
  # Sort of True = 1
  # Certainly True = 2

#### [**SDQ Impacts**]{.underline}

-   cut because data is only from parents and teachers, not the children
    themselves

#### [**Wentzel's**]{.underline}

-   Child Wave 1: C1_AG1 to 4

-   Child Wave 2: C2_AG1 to 4

-   Child Wave 3: C3_AG1 to 4
    
    #Never = 1, Seldom = 2, Sometimes = 3, Often = 4, Always = 5, none to recode

#### [**FSM**]{.underline}

-   "FSM" #0 for no, 1 for yes

#### [**SCQ: School Concerns Questionnaire**]{.underline}

-   Child Wave 1: C1_SConcern1 to 20

-   Child Wave 2: C2_SConcern1 to 20

-   Child Wave 3: C3_SConcern1 to 20
    # just add 1 and 10 bc the others are numbers

#### [**CDPQ: Child Development Project Questionnaire (school liking)**]{.underline}

-   Child Wave 1: N/A

-   Child Wave 2: C2_SL1 to 5 - recode 1, 4

-   Child Wave 3: C3_SL1 to 5 - recode 3, 5
#delete because no wave 1
    
    
#### [**CDPQ: Child Development Project Questionnaire (trust and respect for teachers)**]{.underline}

-   Child Wave 1: C1_LT1 to 10 - recode: 1,3,5,7,9,10

-   Child Wave 2: C2_LT1 to 10 - recode: 1,3,5,7,9,10

-   Child Wave 3: C3_LT1 to 10 - recode: 2,4,6,8
    
    #YES!! = 1, yes = 2, no = 3, NO!! = 4

#### [**LiCs: School-oriented version fo the Loneliness in Children scale**]{.underline}

-   Child Wave 1: C1_L1 to 16 - recode: 1,3,5,7,10,15

-   Child Wave 2: C1_L1,2,6,7,11,14,15 - recode: 1,7,15

-   Child Wave 3: C1_L1,2,6,7,11,14,15 - recode: 1,7,15
    
    #not true at all = 1, hardly ever true = 2, sometimes true = 3, true most of the time = 4, always true = 5

#### [**KS2: English, Maths, Science**]{.underline}

-   "KS2MathstestNUM" - THIS

-   "KS2EnglishtestNUM" - THIS

-   "KS2EnglishTANUM"

-   "KS2EngComb"

#### [**KS3: English, Maths, Science**]{.underline} 

-   "Y7EnglishNC" - THIS

-   "Y7MathsNC" - THIS

-   "Y7ScienceNC"

-   "Y7NC"

-   "Y7EnglishIMYC" 

-   "Y7MathsIMYC" 

-   "Y7ScienceIMYC"

-   "Y7IMYC"

-   "Eng7"

-   "Math7"

-   "Sci7" # no science
}

# NOTE: english and maths are all numbers whatever the numbers mean

# getting all the columns for each measure
cols_sdq <- grep("^C[123]_B[1-25]", names(st_data), value = TRUE)
cols_wen <- grep("^C[123]_AG[1-4]$", names(st_data), value = TRUE)
cols_sqc <- grep("^C[123]_SConcern([1-9]|1[0-9]|20)$", names(st_data), value = TRUE)
cols_sl <- grep("^C[123]_SL[1-5]", names(st_data), value = TRUE)
cols_lt <- grep("^C[123]_LT[1-9]|^C[123]_LT10$", names(st_data), value = TRUE)
cols_lon <- grep("^C[123]_L([1-9]|1[0-5]|15)$", names(st_data), value = TRUE)
cols_ks2 <- c("KS2MathstestNUM", "KS2EnglishtestNUM")
cols_ks3 <- c("Y7EnglishNC", "Y7MathsNC")

# making a variable that has all of the above - this method didn't work though i wanna try finding out how to not hard code the select() line
chosen_vars <- c("X", "ID", cols_sdq, cols_wen, "FSM", cols_sqc, cols_sl, cols_lt, cols_lon, cols_ks2)

# making our df using the chosen variable columns
library(dplyr)

our_data <- st_data %>%
  select("X", "ID", cols_sdq, cols_wen, "FSM", cols_sqc, cols_sl, cols_lt, cols_lon, cols_ks2, cols_ks3)

write.csv(our_data, file = "our_data.csv", row.names = TRUE)
<<<<<<< HEAD
read.csv(our_data, "our_data.csv")


```
 
 

```

```{r}
# relabeling the text value variables with numeric factors
our_data <- our_data %>% 
  mutate(
    C1_B1=factor(C1_B1, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")))

```

```{r}
#### [**Wentzel's**]{.underline}

#-   Child Wave 1: C1_AG1 to 4

#-   Child Wave 2: C2_AG1 to 4

#-   Child Wave 3: C3_AG1 to 4
    
    #Never = 1, Seldom = 2, Sometimes = 3, Often = 4, Always = 5, none to recode

our_data <- our_data %>% 
  mutate(
    C1_B1=factor(C1_B1, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")))


```
>>>>>>> 8f5f03a3a13e31c596621abaa6a4b3feb3f5217f

 
``` {r}

our_data1 <- our_data %>% 
  mutate(
    C1_B1 = factor(C1_B1, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B2 = factor(C1_B2, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B5 = factor(C1_B5, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B10 = factor(C1_B10, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B11 = factor(C1_B11, levels = c(0, 1, 2), labels = c("Certainly true", "Sort of true", "Not true")),
    C1_B12 = factor(C1_B12, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B13 = factor(C1_B13, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B14 = factor(C1_B14, levels = c(0, 1, 2), labels = c("Certainly true", "Sort of true", "Not true")),
    C1_B15 = factor(C1_B15, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B16 = factor(C1_B16, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B17 = factor(C1_B17, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B18 = factor(C1_B18, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B19 = factor(C1_B19, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B20 = factor(C1_B20, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B21 = factor(C1_B21, levels = c(0, 1, 2), labels = c("Certainly true", "Sort of true", "Not true")),
    C1_B22 = factor(C1_B22, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B23 = factor(C1_B23, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B24 = factor(C1_B24, levels = c(0, 1, 2), labels = c("Not true", "Sort of true", "Certainly true")),
    C1_B25 = factor(C1_B25, levels = c(0, 1, 2), labels = c("Certainly true", "Sort of true", "Not true"))
  )

    

 ##C1_B5 4 should be 1
 #C1_B14, 4 should be 2
=======

 ```
